\Large Postdoctoral Position Research Proposal: \\ The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets\vspace{-2ex}

### 2015-12-30 Postdoc Applications/research_proposal_hilke.tex
update

%\usepackage{pdfsync}
%\usepackage{subeqnarray}
\usepackage[top=0.9in, bottom=0.6in, left=1in, right=1in]{geometry}
\usepackage{natbib}
\usepackage{color}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{sectsty}
\usepackage{sidecap}
\usepackage{placeins}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage[font={footnotesize}]{caption}
\setlength{\droptitle}{-7em}
%\setlength{\abovecaptionskip}{-2.5ex}
\setlength{\belowcaptionskip}{-1ex}
%\pagenumbering{gobble}
\pagestyle{fancy}
\lhead{Ana-Maria Piso}
\rhead{Postdoctoral Position in Exoplanet Theory Research Proposal}
\date{}
%\rhead{\thepage}

@@

\title{\Large Postdoctoral Position in Exoplanet Theory Research Proposal: \\
The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets\vspace{-2ex}}
\author{Ana-Maria Piso \vspace{-2ex}}

@@

\textbf{The University of Chicago is the ideal place for me to pursue my postdoctoral research}, due to its vibrant community of experts in protoplanetary disks and exoplanets, both in the Department of Astronomy and Department of Geophysical Sciences. I would love the opportunity to work with \textbf{Prof. Leslie Rogers}, an expert in planetary interiors and atmospheres --- such a collaboration would be instrumental in achieving my research goals during my postdoctoral tenure and afterwards. In the Department of Geophysical Sciences, I would like to collaborate with \textbf{Prof. Fred Ciesla}, a leader in protoplanetary disk dynamics, chemical composition and evolution. Additionally, the Department of Astronomy hosts experts in detecting and characterizing worlds outside the Solar system, such as \textbf{Prof. Dan Fabrycky} and \textbf{Prof. Jacob Bean}, which presents great prospects in connecting my theoretical research work with observations. \\

@@

%\section*{References}
\footnotesize
%\begin{thebibliography} {9}
\noindent $[1]$ Batalha, N. M. 2014, Proceedings of the National Academy of Science, 111, 12647 \\
$[2]$ Lissauer J. J., Dawson R. I., Tremaine S., 2014, Nature, 513, 336 \\
$[3]$ Debes, J. H., Jang-Condell, H., Weinberger, A. J., Roberge, A., \& Schneider, G. 2013, ApJ, 771, 45 \\
$[4]$ Kreidberg, L., Line, M. R., Bean, J. L., et al. 2015, ArXiv e-prints, arXiv:1504.05586 \\
$[5]$ Piso, A.-M. A., \& Youdin, A. N. 2014, ApJ, 786, 21 \\
$[6]$ Piso, A.-M. A., Youdin, A. N., \& Murray-Clay, R. A. 2015, ApJ, 800, 82 \\
$[7]$ Piso, A.-M. A., Öberg, K.I., Birnstiel, T, \& Murray-Clay, R.M., ApJ, resubmitted after referee report \\
$[8]$ ALMA Partnership et al., 2015, ApJ, 808, L3 \\
$[9]$ \"Oberg, K. I., Murray-Clay, R., \& Bergin, E. A. 2011, ApJ, 743, L16 \\
$[10]$ Ida, S., Lin, D. N. C., \& Nagasawa, M. 2013, ApJ, 775, 42 \\
$[11]$ Semenov, D., \& Wiebe, D. 2011, ApJS, 196, 25
%\end{thebibliography}

>>>>

%\usepackage{pdfsync}
%\usepackage{subeqnarray}
\usepackage[top=0.9in, bottom=0.6in, left=1in, right=1in]{geometry}
\usepackage{natbib}
\usepackage{color}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{titling}
\usepackage{sectsty}
\usepackage{sidecap}
\usepackage{placeins}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage[font={footnotesize}]{caption}
\setlength{\droptitle}{-7em}
%\setlength{\abovecaptionskip}{-2.5ex}
\setlength{\belowcaptionskip}{-1ex}
%\pagenumbering{gobble}
\pagestyle{fancy}
\lhead{Ana-Maria Piso}
\rhead{Postdoctoral Position Research Proposal}
\date{}
%\rhead{\thepage}

@@

\title{\Large Postdoctoral Position Research Proposal: \\
The Role of Disk Volatile Chemistry and Dynamics in Shaping the Compositions of Nascent Planets\vspace{-2ex}}
\author{Ana-Maria Piso \vspace{-2ex}}

@@

\textbf{MIT is the ideal place for me to pursue my postdoctoral work.} Its research facilities and academic excellence are unparalleled. I would love the opportunity to work with \textbf{Prof. Hilke Schlichting}, an expert in planet formation theory and dynamics --- such a collaboration would be instrumental in achieving my research goals during my postdoctoral tenure and afterwards. I would also like to collaborate with \textbf{Prof. Sara Seager}, a co-investigator of the TESS mission and a leading theorist in atmospheric chemistry, as well as with members of her group, who specialize in a broad range of exoplanet theory and computational topics. \textbf{Dr. Margaret Pan}, an excellent theorist in planetary dynamics and protoplanetary disks, will join the MIT EAPS department in early 2016 --- it would be a pleasure to work with her as well. Additionally, the MIT Physics department hosts leaders in detecting and characterizing worlds outside the Solar system, such as \textbf{Prof. Joshua Winn}, which presents great prospects in connecting my theoretical research work with observations. \\

%Finally, in order to connect my theoretical work with observations, I would like to collaborate with \textbf{Prof. Joshua Winn}, who is an expert in discovering and characterizing exoplanets. \\

%\textbf{The University of Chicago is the ideal place for me to pursue my postdoctoral research}, due to its vibrant community of experts in protoplanetary disks and exoplanets, both in the Department of Astronomy and Department of Geophysical Sciences. I would love the opportunity to work with \textbf{Prof. Leslie Rogers}, an expert in planetary interiors and atmospheres --- such a collaboration would be instrumental in achieving my research goals during my postdoctoral tenure and afterwards. In the Department of Geophysical Sciences, I would like to collaborate with \textbf{Prof. Fred Ciesla}, a leader in protoplanetary disk dynamics, chemical composition and evolution. Additionally, the Department of Astronomy hosts experts in detecting and characterizing worlds outside the Solar system, such as \textbf{Prof. Dan Fabrycky} and \textbf{Prof. Jacob Bean}, which presents great prospects in connecting my theoretical research work with observations. \\

@@

%\section*{References}
\footnotesize
%\begin{thebibliography} {9}
\noindent $[1]$ Batalha, N. M. 2014, Proceedings of the National Academy of Science, 111, 12647 \\
$[2]$ Lissauer J. J., Dawson R. I., Tremaine S., 2014, Nature, 513, 336 \\
$[3]$ Debes, J. H., Jang-Condell, H., Weinberger, A. J., Roberge, A., \& Schneider, G. 2013, ApJ, 771, 45 \\
$[4]$ Kreidberg, L., Line, M. R., Bean, J. L., et al. 2015, ApJ, 814, 66 \\
$[5]$ Piso, A.-M. A., \& Youdin, A. N. 2014, ApJ, 786, 21 \\
$[6]$ Piso, A.-M. A., Youdin, A. N., \& Murray-Clay, R. A. 2015, ApJ, 800, 82 \\
$[7]$ Piso, A.-M. A., \"Oberg, K. I. , Birnstiel, T., \& Murray-Clay, R. A. 2015, ApJ, 815, 109 \\
$[8]$ ALMA Partnership et al., 2015, ApJ, 808, L3 \\
$[9]$ \"Oberg, K. I., Murray-Clay, R., \& Bergin, E. A. 2011, ApJ, 743, L16 \\
$[10]$ Ida, S., Lin, D. N. C., \& Nagasawa, M. 2013, ApJ, 775, 42 \\
$[11]$ Semenov, D., \& Wiebe, D. 2011, ApJS, 196, 25
%\end{thebibliography}
